Slitasje og kjørespor

### 2023-01-18 DRAFT_slitasjeOgKjørespor.Rmd
feat: Indicators per region and HIF class

ggplot(temp, aes(x = region, y = area, fill = factor(infrastructureIndex)))+
  geom_bar(position = "stack", stat = "identity")
```

The figure above shows that Nord-Norge for example, has a lot of relatovely untouched areas, and that Østlandet has the highets proportion of impacted areas.
This is expected.

@@

```{r}
eaTools::ea_spread()
```

>>>>

ggplot(temp, aes(x = region, y = area, fill = factor(infrastructureIndex)))+
  geom_bar(position = "stack", stat = "identity")+
  guides(fill = guide_legend("HIF"))
```

The figure above shows that Nord-Norge for example, has a lot of relatively untouched areas, and that Østlandet has the highest proportion of impacted areas.
This is expected. 
<!-- It also shows that the second HIF class is perhaps to narrowly defined. This is suggested as a change in another PR: -->

@@

```{r, eval=F}
slitasje_data_extrapolated <- ea_spread(indicator_data = slitasje_data,
                         indicator = i_2020,
                         regions = HIA_regions,
                         groups = region_HIF,
                         threshold = 20)
saveRDS(slitasje_data_extrapolated, "P:/41201785_okologisk_tilstand_2022_2023/data/cache/slitasje_data_extrapolated.rds")
```

```{r, echo=F}
# silently read cached file
slitasje_data_extrapolated <- readRDS("P:/41201785_okologisk_tilstand_2022_2023/data/cache/slitasje_data_extrapolated.rds")
```

```{r}
unique(slitasje_data_extrapolated$meanIndicatorValue)
```
<!-- slitasje_data_extrapolated contains 32402 rows, but I expected 5. -->

<!-- Like this: -->
```{r, eval=F}
slitasje_data_extrapolated2 <- ea_spread(indicator_data = slitasje_data_extrapolated,
                         indicator = meanIndicatorValue,
                         regions = regions,
                         groups = region,
                         threshold = 20)
saveRDS(slitasje_data_extrapolated2, "P:/41201785_okologisk_tilstand_2022_2023/data/cache/slitasje_data_extrapolated2.rds")
```
```{r, echo=F}
# silently read cached file
slitasje_data_extrapolated2 <- readRDS("P:/41201785_okologisk_tilstand_2022_2023/data/cache/slitasje_data_extrapolated2.rds")
```

```{r}
plot(factor(slitasje_data_extrapolated2$ID), slitasje_data_extrapolated2$meanIndicatorValue,
     ylab="indicator value", xlab="", ylim=c(0,1))
```
